---
title: "Sequential"
author: "185314135_DharuJiwoPambudi"
date: "25/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


#Import Library
```{r}
library(dplyr);
```

```{r}
library(tidyverse)
```

```{r}
library(arulesSequences)
```

#Import Data
{r}

#Import standard transaction data
```{r}
transactions = read.csv("datasequential.csv",sep=";")
```


```{r}
transactions$Invoice <- as.Date(transactions$InvoiceDate)
transactions
```


#Start time of data to be considered
{r}
```{r}
start_month <- "2021-03-01"
```


#Create list by customer ID and InvoiceDate (formatted dates)
{r}
```{r}
trans_sequence <- transactions %>%
    group_by(CustomerID, InvoiceDate) %>%
    summarize(
        SIZE = n(),
        ItemSet = paste(as.character(StockCode), collapse = ';')
    )
```




#Make event and sequence IDs into factors
{r}
```{r}
elapsed_months <- function(end_date, start_date) {
    ed <- as.POSIXlt(end_date)
    sd <- as.POSIXlt(start_date)
    12 * (ed$year - sd$year) + (ed$mon - sd$mon)
}
```
```{r}
#trans_sequence$eventID <- elapsed_months(trans_sequence$InvoiceDate, start_month)
trans_sequence$eventID <- trans_sequence$InvoiceDate
```




#Mengubah urutan tampilan

```{r}
trans_sequence = trans_sequence[,c(1,5,3,4)]
names(trans_sequence) = c("sequenceID", "eventID", "SIZE", "items")

trans_sequence <- data.frame(lapply(trans_sequence, as.factor))
trans_sequence <- trans_sequence[order(trans_sequence$sequenceID, trans_sequence$eventID),]

trans_sequence
```


#Convert to transaction matrix data type
{r}
```{r}
write.table(trans_sequence, "mytxtout.txt", sep=";", row.names = FALSE, col.names = FALSE, quote = FALSE)

```


{r}
```{r}
trans_matrix <- read_baskets("mytxtout.txt", sep = ";", info = c("sequenceID","eventID","SIZE"))

trans_matrix

inspect(trans_matrix)
```



#Penggunaan algoritme SPADE
{r}
freq1 <- cspade(trans_matrix, parameter = list(support = 0.3), control = list(verbose = TRUE))

{r}
freq1.df <- as(freq1, "data.frame")
freq1.df


#Menampilkan rule
{r}
r1 <- as(ruleInduction(freq1, confidence = 0.5, control = list(verbose = TRUE)), "data.frame")
r1

#Membaca

```{r}
trans_matrix1 <- read_baskets("datasequentiall.txt", sep = ";", info = c("sequenceID","eventID","SIZE"))


inspect(trans_matrix1)
```

##Mencari Spade
```{r}
freq1 <- cspade(trans_matrix1, parameter = list(support = 0.4), control = list(verbose = TRUE))

freq1.df <- as(freq1, "data.frame")
freq1.df
```

#Menampilkan rule
```{r}
r1 <- as(ruleInduction(freq1, confidence = 0.5, control = list(verbose = TRUE)), "data.frame")
r1
```




